\pkg{plotROC}: A Better Tool for Plotting ROC Curves

### 2015-02-02 Paper/sachs2014plotROC.Rmd
typo
added qtlcharts reference

I created a \pkg{shiny} application [@shiny] in order to make the features more accessible to non-\proglang{R} users. A limited subset of the functions of the \pkg{plotROC} can be performed on an example dataset or on data that users upload to the website. Resulting plots can be saved to the users' machine as a pdf or as a stand-alone html file.  It can be used in any modern web browser with no other dependencies at the website here: http://sachsmc.shinyapps.io/plotROC.

@@

This approach is similar to what is done in the \pkg{gridSVG} `grid.animate` function, which uses the svg `<animate />` tags. However, the available features were not sufficient for my needs, which is why I used \pkg{d3.js}. There are several other \proglang{R} packages that aim to create interactive figures. The authors of \pkg{animint} [@animint] created an extensive \proglang{JavaScript} library that creates plots in a similar way as \pkg{ggplot2}. A set of interactive features can be added to plots using \pkg{d3.js}. \pkg{ggvis} [@ggvis], \pkg{rCharts} [@rcharts], and the more recently released \pkg{htmlwidgets} [@htmlwidgets] all leverage existing charting libraries written in \proglang{JavaScript}. Their general approach is to manipulate the data and create options in \proglang{R}, and then let the charting libraries handle the rendering and interactivity. \pkg{plotROC} lets \proglang{R} do the rendering, allowing the figures to be consistent across print and web-based media, and retaining the distinctive \proglang{R} style.

@@

>>>>

I created a \pkg{shiny} application [@shiny] in order to make the features more accessible to non-\proglang{R} users. A limited subset of the functions of \pkg{plotROC} can be performed on an example dataset or on data that users upload to the website. Resulting plots can be saved to the users' machine as a pdf or as a stand-alone html file.  It can be used in any modern web browser with no other dependencies at the website here: http://sachsmc.shinyapps.io/plotROC.

@@

This approach is similar to what is done in the \pkg{gridSVG} `grid.animate` function, which uses the svg `<animate />` tags. However, the available features were not sufficient for my needs, which is why I used \pkg{d3.js}. There are several other \proglang{R} packages that aim to create interactive figures. The authors of \pkg{animint} [@animint] created an extensive \proglang{JavaScript} library that creates plots in a similar way as \pkg{ggplot2}. A set of interactive features can be added to plots using \pkg{d3.js}. \pkg{ggvis} [@ggvis], \pkg{rCharts} [@rcharts], and the more recently released \pkg{htmlwidgets} [@htmlwidgets] all leverage existing charting libraries written in \proglang{JavaScript}. \pkg{qtlcharts} [@qtlcharts] uses a set of custom \proglang{JavaScript} and \pkg{d3.js} functions to visualize data from genetic experiments. Their general approach is to manipulate the data and create options in \proglang{R}, and then let the charting libraries or functions handle the rendering and interactivity. \pkg{plotROC} lets \proglang{R} do the rendering, allowing the figures to be consistent across print and web-based media, and retaining the distinctive \proglang{R} style. This also allows users to manipulate the figures directly in \proglang{R} to suit their needs, using tools that are more accessible and familiar to most \proglang{R} users.

@@

## Reproducibility Note

This manuscript is completely reproducible using the source files available at http://github.com/sachsmc/plotROC-paper. The output below indicates the \proglang{R} packages and versions used. Compiling the pdf output also requires `pandoc` version 1.13.1 and `pdflatex`.

```{r sesh}
sessionInfo()
```

### 2015-02-02 Paper/sachs2014plotROC.tex
typo
added qtlcharts reference

I created a \pkg{shiny} application \citep{shiny} in order to make the
features more accessible to non-\proglang{R} users. A limited subset of
the functions of the \pkg{plotROC} can be performed on an example
dataset or on data that users upload to the website. Resulting plots can
be saved to the users' machine as a pdf or as a stand-alone html file.
It can be used in any modern web browser with no other dependencies at
the website here: http://sachsmc.shinyapps.io/plotROC.

@@

This approach is similar to what is done in the \pkg{gridSVG}
\texttt{grid.animate} function, which uses the svg
\texttt{\textless{}animate /\textgreater{}} tags. However, the available
features were not sufficient for my needs, which is why I used
\pkg{d3.js}. There are several other \proglang{R} packages that aim to
create interactive figures. The authors of \pkg{animint} \citep{animint}
created an extensive \proglang{JavaScript} library that creates plots in
a similar way as \pkg{ggplot2}. A set of interactive features can be
added to plots using \pkg{d3.js}. \pkg{ggvis} \citep{ggvis},
\pkg{rCharts} \citep{rcharts}, and the more recently released
\pkg{htmlwidgets} \citep{htmlwidgets} all leverage existing charting
libraries written in \proglang{JavaScript}. Their general approach is to
manipulate the data and create options in \proglang{R}, and then let the
charting libraries handle the rendering and interactivity. \pkg{plotROC}
lets \proglang{R} do the rendering, allowing the figures to be
consistent across print and web-based media, and retaining the
distinctive \proglang{R} style.

@@

>>>>

I created a \pkg{shiny} application \citep{shiny} in order to make the
features more accessible to non-\proglang{R} users. A limited subset of
the functions of \pkg{plotROC} can be performed on an example dataset or
on data that users upload to the website. Resulting plots can be saved
to the users' machine as a pdf or as a stand-alone html file. It can be
used in any modern web browser with no other dependencies at the website
here: http://sachsmc.shinyapps.io/plotROC.

@@

This approach is similar to what is done in the \pkg{gridSVG}
\texttt{grid.animate} function, which uses the svg
\texttt{\textless{}animate /\textgreater{}} tags. However, the available
features were not sufficient for my needs, which is why I used
\pkg{d3.js}. There are several other \proglang{R} packages that aim to
create interactive figures. The authors of \pkg{animint} \citep{animint}
created an extensive \proglang{JavaScript} library that creates plots in
a similar way as \pkg{ggplot2}. A set of interactive features can be
added to plots using \pkg{d3.js}. \pkg{ggvis} \citep{ggvis},
\pkg{rCharts} \citep{rcharts}, and the more recently released
\pkg{htmlwidgets} \citep{htmlwidgets} all leverage existing charting
libraries written in \proglang{JavaScript}. \pkg{qtlcharts}
\citep{qtlcharts} uses a set of custom \proglang{JavaScript} and
\pkg{d3.js} functions to visualize data from genetic experiments. Their
general approach is to manipulate the data and create options in
\proglang{R}, and then let the charting libraries or functions handle
the rendering and interactivity. \pkg{plotROC} lets \proglang{R} do the
rendering, allowing the figures to be consistent across print and
web-based media, and retaining the distinctive \proglang{R} style. This
also allows users to manipulate the figures directly in \proglang{R} to
suit their needs, using tools that are more accessible and familiar to
most \proglang{R} users.

@@

\subsection{Reproducibility Note}\label{reproducibility-note}

This manuscript is completely reproducible using the source files
available at http://github.com/sachsmc/plotROC-paper. The output below
indicates the \proglang{R} packages and versions used. Compiling the pdf
output also requires \texttt{pandoc} version 1.13.1 and
\texttt{pdflatex}.

\begin{verbatim}
sessionInfo()
\end{verbatim}

\begin{verbatim}
R version 3.1.2 (2014-10-31)
Platform: x86_64-apple-darwin13.4.0 (64-bit)

locale:
[1] en_US.UTF-8/en_US.UTF-8/en_US.UTF-8/C/en_US.UTF-8/en_US.UTF-8

attached base packages:
[1] methods   stats     graphics  grDevices utils     datasets  base

other attached packages:
[1] DiagrammeR_0.3   ggplot2_1.0.0    tikzDevice_0.7.0 filehash_2.2-2  
[5] plotROC_1.3.2    xtable_1.7-4     stringr_0.6.2    knitr_1.8

loaded via a namespace (and not attached):
 [1] colorspace_1.2-4  digest_0.6.8      evaluate_0.5.5   
 [4] formatR_1.0.3     grid_3.1.2        gtable_0.1.2     
 [7] htmltools_0.2.6   htmlwidgets_0.3.2 MASS_7.3-35      
[10] munsell_0.4.2     plyr_1.8.1        proto_0.3-10     
[13] Rcpp_0.11.3       reshape2_1.4.1    RJSONIO_1.3-0    
[16] rstudioapi_0.2    scales_0.2.4      tools_3.1.2      
[19] yaml_2.1.13      
\end{verbatim}
